FTLR proof cases

### 2018-03-07 fully-abstract-comp/ftlr-proof-cases.tex
Some work on a lemma about the read and write condition. Add some remarks about problems with spurious later modalities.

\maketitle
\section{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[$\lrv$ mono]
  For all $n$, $w_1$, $w_2$, and $W' \future W$, if $\npair{(w_1,w_2)} \in \lrv(W)$, then $\npair{(w_1,w_2)} \in \lrv(W')$
\end{lemma}

@@

@@

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{[(c,c)]} \in \lrp(W)$
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined.
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
Let $i \leq n'$ be given \footnote{ignoring the frame...} and show
\[
  \Phi_S \term[i] \Rightarrow \Phi_T \term
\]
and 
\[
  \Phi_T \term[i] \Rightarrow \Phi_S \term
\]

\subsubsection*{Assuming source machine terminates}
First show the former of the two, assume $\Phi_S\term[i]$. We now consider the first step of $\Phi_S \term[i]$\footnote{if $i=0$, then we have a contradiction with $\Phi_S\term[i]$.}. 
The possible instructions that could have been executed are:
\begin{enumerate}
\item $\txjmp{r_1}{r_2}$
\item $\scall[o]{}{r_1}{r_2}$
\end{enumerate}

@@

>>>>

\maketitle
\section{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[$\lrv$ mono]
  For all $n$, $w_1$, $w_2$, and $W' \future W$, if $\npair{(w_1,w_2)} \in \lrv(W)$, then $\npair{(w_1,w_2)} \in \lrv(W')$.
\end{lemma}

@@

\begin{lemma}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $\npair{(b,e)}\in\readCond{l,W}$
  \item $a \in [b,e]$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \end{itemize}
  Then $\npair[n']{(\ms_S(a),\ms_T(a))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.
  Additionally, if
  \begin{itemize}
  \item $\npair{(b,e)}\in\writeCond{l,W}$
  \end{itemize}
  Then $\memSat{(\ms_S[a\mapsto 0],\stk,\ms_\stk,\ms_T[a\mapsto 0])}{W_M'}$.
\end{lemma}
\begin{proof}
  From $\npair{(b,e)}\in\readCond{l,W}$, we get an $r \in \addressable{\lin,
    \pwheap}$ and $[\baddr',\eaddr'] \supseteq [\baddr,\eaddr]$ such that $\pwheap(r)
  \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}$.

  Since $W \oplus W_M$ is defined, we have that $r \in \dom(\pwheap) =
  \dom(\pwheap[W_M])$ and $\pwheap(r) \oplus \pwheap[W_M](r)$ is defined.

  From $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$, we get that
  $\stk = (\opc_0,\ms_0):: \dots :: (\opc_m,\ms_m)$,
  $\ms_S \uplus \ms_\stk \uplus \ms_0 \uplus \dots \uplus \ms_m$,
  $W_M = W_{\var{stack}} \oplus W_{\var{free\_stack}} \oplus W_{\var{heap}}$ and
  $\exists \ms_\var{T,stack}, \ms_\var{T,free\_stack}, \ms_\var{T,heap}$ such that
  \begin{itemize}
  \item $\ms_T = \ms_\var{T,stack} \uplus \ms_\var{T,free\_stack} \uplus
    \ms_\var{T,heap}$
  \item $\memSatStack{\stk,\ms_\var{T,stack}}{W_{\var{stack}}}$
  \item $\memSatFStack{\ms_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}}$
  \item $\memSatHeap{\ms_S,\ms_\var{T,heap}}{W_\var{heap}}$.
  \end{itemize}

  From $\memSatHeap{\ms_S,\ms_\var{T,heap}}{W_\var{heap}}$, we get an
  $R_\ms : \dom(\activeReg{\pwheap[W_\var{heap}]}) \fun \MemSeg \times \MemSeg$,
  $\ms_\var{T,heap} = \biguplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} \pi_2(R_\ms(r))$,
  $\ms_S = \biguplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} \pi_1(R_\ms(r))$,
  $\exists R_W : \dom(\activeReg{\pwheap[W_\var{heap}]}) \fun \World\ldotp$
  $W_\var{heap} = \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} R_W(r)$,
  $\forall r \in \activeReg{\pwheap[W_\var{heap}]}, n' < n$, we have that
  $\npair[n']{R_\ms(r)} \in  \pwheap[W_\var{heap}](r).H \; \pwheap[W_\var{heap}](r).s \; \xi^{-1}(R_W(r))$.

  We have that $r \in \addressable{\lin, \pwheap} \subseteq
  \activeReg{\pwheap[W_\var{heap}]}$, so $\npair[n']{R_\ms(r)} \in
  \pwheap[W_\var{heap}](r).H \; \pwheap[W_\var{heap}](r).s \; \xi^{-1}(R_W(r))$.
  Because $\pwheap(r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}$ and $W\oplus W_M = W \oplus (W_\var{heap} \oplus W_\var{free\_stack} \oplus W_\var{stack})$ is defined, it follows that
  also $\pwheap[W_\var{heap}](r) \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}$ this
  means that also $\npair[n']{R_\ms(r)} \in
  H^{\mathrm{std}}_{[\baddr',\eaddr']}\; \xi^{-1}(R_W(r))$.

  From this, it follows that $\dom(R_\ms(r).1) = \dom(R_\ms(r).2) = [\baddr',\eaddr']$ and we get a $S : [\baddr',\eaddr'] \fun \World$ with $\xi(\xi^{-1}(R_W(r))) = \oplus_{\aaddr \in [\baddr',\eaddr']} S(\aaddr)$ and $\forall \aaddr \in [\baddr',\eaddr'] \ldotp \npair[n'-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$.
  \dominique{TODO: get rid of n'-1 above somehow.}

  Since $a \in [b,e] \subseteq [\baddr',\eaddr']$, we have that $\npair[n'-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$ and
  we can take $W_M' = W_r' \oplus W_{\var{heap}}' \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})$ with $W_r' = \oplus_{\aaddr \in ([\baddr',\eaddr']\setminus \{\aaddr\})} S(\aaddr)$ and $W_\var{heap}' = \oplus_{r' \in (\dom(\activeReg{\pwheap[W_\var{heap}]})\setminus \{r\})} R_W(r')$, and get
  \begin{align*}
    S(\aaddr) \oplus W_M'
    &=S(\aaddr) \oplus (W_r' \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}}))\\
    &=
    \oplus_{\aaddr \in [\baddr',\eaddr']} S(\aaddr) \oplus W_{\var{heap}}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    \xi(\xi^{-1}(R_W(r))) \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    R_W(r) \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} R_W(r)\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
      W_\var{heap} \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
      &= W_M
  \end{align*}

  Additionally, if $\npair{(b,e)}\in\writeCond{l,W}$, then
  we get an $r' \in \addressable{\lin, \pwheap} \subseteq \activeReg{\pwheap[W_\var{heap}]}$
  and $[\baddr',\eaddr'] \supseteq [\baddr,\eaddr]$ such that
  $\pwheap(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur}$ and
  $\pwheap(r) \text{ is address-stratified}$. Because $W \oplus W_M$ is defined, it follows that also 
  $\pwheap[W_\var{heap}](r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur}$ and
  $\pwheap[W_\var{heap}](r) \text{ is address-stratified}$.
  \dominique{TODO: get rid of n-1 above.}

  It follows that $r = r'$ because $\dom(R_\ms(r).1) = \dom(R_\ms(r).2) = [\baddr',\eaddr'] = \dom(R_\ms(r').2) = \dom(R_\ms(r').1)$ and all the $R_\ms(r).1$ and $R_\ms(r).2$ are disjoint.

  We have that $\npair[n']{(R_\ms(r).1\update{a}{0},R_\ms(r).2\update{a}{0})} \in \pwheap[W_\var{heap}](r).H \;
  \pwheap[W_\var{heap}](r).s \; \xi^{-1}(W_r')$ because $\pwheap[W_\var{heap}](r)$ is address-stratified and $\pwheap[W_\var{heap}](r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr']}{\pur}$.

  From this, it follows that $\memSatHeap{\ms_S\update{a}{0},\ms_\var{T,heap}\update{a}{0}}{W_r' \oplus W_\var{heap}'}$ and finally $\memSat{(\ms_S\update{a}{0},\stk,\ms_\stk,\ms_T\update{a}{0})}{W_M'}$.
\end{proof}

@@

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{[(c,c)]} \in \lrp(W)$ \dominique{Weird that this is an assumption here.  Shouldn't this be a proof obligation? Or rather: I think this should not be here at all but in the value relation instead? Remove this from the definition of $\lre$?}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined.
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
Let $i \leq n'$ be given \footnote{ignoring the frame...} and show
\[
  \Phi_S \term[i] \Rightarrow \Phi_T \term
\]
and 
\[
  \Phi_T \term[i] \Rightarrow \Phi_S \term
\]

\subsubsection*{Assuming source machine terminates}
First show the former of the two, assume $\Phi_S\term[i]$. We now consider the first step of $\Phi_S \term[i]$\footnote{if $i=0$, then we have a contradiction with $\Phi_S\term[i]$.}. 
The possible instructions that could have been executed are:
\begin{enumerate}
\item $\tfail$
\item $\thalt$
\item $\tjmp{\trg{r_1}}$
\item $\tjnz{\trg{r_1}}{\trg{\rn}}$
\item $\tisptr{\trg{r_1}}{\trg{r_2}}$
\item $\tgeta{\trg{r_1}}{\trg{r_2}}$
\item $\tgetb{\trg{r_1}}{\trg{r_2}}$
\item $\tgetp{\trg{r_1}}{\trg{r_2}}$
\item $\tgetlin{\trg{r_1}}{\trg{r_2}}$
\item $\tmove{\trg{r_1}}{\trg{\rn}}$
\item $\tstore{\trg{r_1}}{\trg{r_2}}$
\item $\tload{\trg{r_1}}{\trg{r_2}}$
\item $\tcca{\trg{r_1}}{\trg{\rn}}$
\item $\trestrict{\trg{r_1}}{\trg{r_2}}{\trg{\rn}}$
\item $\tlt{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tplus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tminus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tsetatob{\trg{r_1}}{\trg{r_2}}$
\item $\txjmp{\trg{r_1}}{\trg{r_1}}$
\item $\tcseal{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$
\item $\tsplice{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$
\item $\scall[o]{}{r_1}{r_2}$
\end{enumerate}

\paragraph{Case: $\protect\tfail$}
Contradiction, because then $\Phi_S \step \failed \not\nstep[i-1] \halted$.

\paragraph{Case: $\protect\thalt$}

\paragraph{Case: $\protect\tjmp{\trg{r}}$}

\paragraph{Case: $\protect\tjnz{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tisptr{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tgeta{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tgetb{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tgete{\trg{r}}{\trg{r}}\mid$}

\paragraph{Case: $\protect\tgetlin{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tmove{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tstore{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tload{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tcca{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\trestrict{\trg{r}}{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tlt{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsetatob{\trg{r}}{\trg{r}}$}

@@

\paragraph{Case: $\protect\tcseal{\trg{r}}{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tsplit{\trg{r}}{\trg{r}}{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsplice{\trg{r}}{\trg{r}}{\trg{r}}$}
